Title

### 2018-09-01 thesis/paper/paper.tex
Improved multi-value

\subsection{Multi-value (Q21510857)}
\paragraph{Constraint}
The multi-value constraint specifies that the constrained property should appear in multiple statements of an item or none.

\begin{table}[H]
\caption{Multi-value constraint (Q21510857)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Required data & item statement \\
\hline
Violation & \makecell{constrained item with exactly one constrained statement} \\
\hline
Dependency & all item statements \\
\hline
Rule features & count \\
\hline
\end{tabularx}
\end{table}

To model this constraint a count of statements using the constrained property per item would be needed. Then a violation would be any constrained item with a count of one for the constrained property. Since there is no need for arbitrarily large counts, but only for the difference between one and two, this could be solved explicitly.

\paragraph{Rules}
The multi-value constraint requires a limited count of constrained statements. Alternatively, it could be said that if the item requires a second statement, the constraint is violated. Pre-processing extracts all items statements and inequality between all item statement properties as usual and the conjunction is 
\begin{equation*}
\begin{split}
c = &\text{statement\_EDB}(Q, I, \text{propertyConstant}, X) \wedge{} \\
&\text{statement\_EDB}(S, I, P, V) \wedge \text{unequal}(\text{propertyConstant}, P)
\end{split}
\end{equation*}
The predicate require\_second\([2]\) is introduced with the same meaning as require except that it will be applied after a required property has been found:
\begin{equation*}
\begin{split}
\text{require\_second}&(S, \text{propertyConstant}, \text{propertyConstant}) \leftarrow \\
&\text{next}(R, S) \wedge \text{statement\_EDB}(R, I, \text{propertyConstant}, C) \wedge{} \\
&\text{next}(Q, R) \wedge \text{require}(Q, \text{propertyConstant}, \text{propertyConstant})  \wedge c
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{require\_second}&(S, \text{propertyConstant}, \text{propertyConstant}) \leftarrow \text{next}(R, S) \wedge{} \\
&\text{require\_second}(R, \text{propertyConstant}, \text{propertyConstant}) \wedge c
\end{split}
\end{equation*}
A violations would be any last statement requiring a second constrained statement.\\

>>>>

\subsection{Multi-value (Q21510857)}
\paragraph{Constraint}
The \emph{multi-value} constraint specifies that the constrained property should appear in multiple statements of an item or none.

\begin{table}[H]
\caption{Multi-value constraint (Q21510857)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Required data & item statements \\
\hline
Violation & \makecell{constrained item with exactly one constrained statement} \\
\hline
Dependency & all item statements \\
\hline
Rule features & count \\
\hline
\end{tabularx}
\end{table}

\paragraph{Rules}
The \emph{multi-value} constraint requires a limited count of constrained statements. Alternatively, it could be said that if the item requires a second statement, the constraint is violated. Inequality is established between all properties of statements and the conjunction is:
\begin{equation*}
\begin{split}
c = &\text{statement\_EDB}(Q, I, \text{propertyConstant}, X) \wedge{} \\
&\text{statement\_EDB}(S, I, P, V) \wedge \text{unequal}(\text{propertyConstant}, P)
\end{split}
\end{equation*}
The predicate require\_second\([2]\) is introduced with the same meaning as require except that it will be applied after a required property has been found:
\begin{equation*}
\begin{split}
\text{require\_second}&(S, \text{propertyConstant}, \text{propertyConstant}) \leftarrow \\
&\text{next}(R, S) \wedge \text{statement\_EDB}(R, I, \text{propertyConstant}, C) \wedge{} \\
&\text{next}(Q, R) \wedge \text{require}(Q, \text{propertyConstant}, \text{propertyConstant})  \wedge c
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{require\_second}&(S, \text{propertyConstant}, \text{propertyConstant}) \leftarrow \text{next}(R, S) \wedge{} \\
&\text{require\_second}(R, \text{propertyConstant}, \text{propertyConstant}) \wedge c
\end{split}
\end{equation*}
A violations would be any last statement requiring a second constrained statement.\\
